An Exploration of Analysis Methods on Predictive Models of Student Success

### 2024-10-21 paper/paper.tex

            \subsubsection{Main to First30}
                A great deal of research exists which utilizes predictive modeling to enhance the learning experience.
                This information could be used to intervene positively impact students' lives, increasing graduation rates.
                For my project, I decided to predict course outcome.
                This information is most useful when it can be predicted early, which is why I limited the data used for predictions to the first 30 days from the start of the course.
                I also excluded data relating to students who dropped out before the 30 day mark so that their lack of data for certain features wouldn't impact the training process.
                \newline
                I therefore decided to 
                Difference in proportion from Main to First30 for 
                Shown demographics
                Final Outcomes
                LAnding to Main Database schema decisions
                Main to First30 Database schema decisions

>>>>

            \subsubsection{Main to First30}
                A great deal of research exists which utilizes predictive modeling to enhance the learning experience.
                This information could be used to intervene positively impact students' lives, increasing graduation rates.
                For my project, I decided to predict course outcome.
                This information is most useful when it can be predicted early, which is why I limited the data used for predictions to the first 30 days from the start of the course.
                I also excluded data relating to students who dropped out before the 30 day mark so that their lack of data for certain features wouldn't impact the training process.
                \newline
                I therefore decided to 
                Difference in proportion from Main to First30 for 
                Shown demographics
                Final Outcomes
                Landing to Main Database schema decisions
                Main to First30 Database schema decisions
